The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-02-19 main.tex
add new panel to figure with num contributors per month. fixes #150

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open-source software license and is free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering the barriers to entry.

@@

\begin{figure}
\includegraphics[width=\textwidth]{ncommits.pdf}
\caption{%
    \emph{Left panel}: Distribution of number of commits per committer.
    \emph{Right panel}: Cumulative number of commits to the \astropypkg core
    package over time.
    \label{fig:ncommits}
}
\end{figure}

@@

Different funding models have been proposed for support of \astropy
(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open-source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.

>>>>

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open source software license and is free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering the barriers to entry.

@@

\begin{figure}
\includegraphics[width=\textwidth]{commits.pdf}
\caption{%
    \emph{Left panel}: Distribution of number of commits per committer.
    \emph{Middle panel}: Cumulative number of commits to the \astropypkg core
    package over time.
    \emph{Right panel}: Number of unique committers per month to the
    \astropypkg core package.
    \label{fig:ncommits}
}
\end{figure}

@@

Different funding models have been proposed for support of \astropy
(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.} organization. NumFOCUS has, to date, covered the direct costs incurred by the \astropy project.
